Effects of Reynolds Number on the Energy Conversion and Near-Wake Dynamics of a High Solidity Vertical-Axis Cross-Flow Turbine

### 2015-12-16 paper.tex
Explain larger error bars at low speed; resolves #71

Mean power and drag coefficients at $\lambda=1.9$ are plotted versus Reynolds
number in Figure~\ref{fig:perf-Re-dep}. There is a drastic improvement in $C_P$
with increasing Reynolds number at lower values of Reynolds number. The power
coefficient then becomes  essentially $Re$-independent at $Re_D = 0.8 \times
10^6$, which corresponds to an approximate average blade chord Reynolds number
$Re_{c, \mathrm{ave}} = 2.1 \times 10^5$. This threshold is consistent with the
behavior of the blade boundary layer transitioning from laminar to turbulent,
thereby promoting either the suppression or reattachment of the laminar
separation bubble \cite{Lissaman1983}.

@@

\caption{UNH-RVAT measured mean power (left) and drag (right) coefficients at
    $\lambda=1.9$ plotted versus Reynolds number.}

>>>>

Mean power and drag coefficients at $\lambda=1.9$ are plotted versus Reynolds
number in Figure~\ref{fig:perf-Re-dep}. Note that the large error bars for $C_P$
at low $Re$ are dominated by systematic error estimates for the torque
transducer, since torque values are at the lower end of the measurement range.
However, the uncertainty due to random error or repeatability remains relatively
low. There is a drastic improvement in $C_P$ with increasing Reynolds number at
lower values of Reynolds number. The power coefficient then becomes  essentially
$Re$-independent at $Re_D = 0.8 \times 10^6$, which corresponds to an
approximate average blade chord Reynolds number $Re_{c, \mathrm{ave}} = 2.1
\times 10^5$. This threshold is consistent with the behavior of the blade
boundary layer transitioning from laminar to turbulent, thereby promoting either
the suppression or reattachment of the laminar separation bubble
\cite{Lissaman1983}.

@@

\caption{UNH-RVAT measured mean power (left) and drag (right) coefficients at
    $\lambda=1.9$ plotted versus Reynolds number. Error bars indicate expanded
    uncertainty estimates for 95\% confidence, which for $C_P$ is dominated by
    systematic error estimates from the torque transducer operating at the lower end
    of its measurement range.}
